---
title: "readme"
output: github_document
date: "2025-02-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## README

This is a README file for codominance project:

```{r}
library(tidyverse)
df_file <- tibble(file = c("`code/analysis_q1.R`",
                           "`code/format_data.R`",
                           "`code/map_mode.R`",
                           "`code/allTraits_mergeFile.R`",
                           "`code/sample_gawdist`"),
                  note = c("multinomial model relating # of codominance to envrionmental variables",
                           "entry point of data formatting; combining all codominance data.",
                           "generating source information for GIS",
                           "getting all trait data together",
                           "sample code for calculating dendrogram trait distance gawdist()"))


```


- analysis_q1: multinomial model relating # of codominance to envrionmental variables
- format_data: entry point of data formatting; combining all codominance data.
- map_mode: generating source information for GIS
- allTraits_mergeFile: getting all trait data together
- sample_gawdist: sample code for calculating dendrogram trait distance gawdist()